---
title: "chooseRandomSGSamples"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load/Install Packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
packages <- c('sjPlot', 'reshape2', 'magrittr', 'data.table', 'gridExtra', 'ggplot2','stringr','readxl','gridExtra','ggpubr','tidyverse', 'dplyr','tidyr','strex','tibble','chron','lubridate','anytime','hms')
ipak(packages)

```

Given the data catalog (https://docs.google.com/spreadsheets/d/1Xs5jM9yGRmRbrSxjrRFIUpzbfb-MdcGOi_FyJen6MXk)
Generate random 3-minute samples under the following constraints
- must have a small-group start and end time
- small-group duration must be greater than sample duration
- must sample evenly across teachers
- must sample randomly across groups, omitting those without student names
- must sample randomly across lessons

```{r options}
opts.NperTeacher = 4
opts.Duration = 180 # seconds

sheets <- excel_sheets('../Data File Catalog_2021-12-13.xlsx')
enrollment_check <- read_xlsx('../Data File Catalog_2021-12-13.xlsx', sheet = 'Enrollment Check')
audio_sheets <- sheets %>% str_subset(pattern = "Audio")
```



```{r loop_over_teachers}
sample_all <- data.frame()
stats.wide.SGduration <- list()
count=0
dtypes = c('text', 'text',
           'text', 'text',
           'text', 'text',
           'text',  'date',   'date','date',
           'date','guess','guess','guess',
           'guess','date',  'list','text','text','guess','guess','logical','text')

for (sheet in audio_sheets){
  count=count+1
  df <- read_xlsx('../Data File Catalog_2021-12-13.xlsx', sheet = sheet, na=c('','NA','Unknown'), col_types = dtypes, trim_ws=T)
  names(df) <- names(df) %>% make.names() 
  if (nrow(df) == 0) next
  
  df <- df %>% filter(!grepl('End',Group.End.Time))
  
  if (class(df$Group.End.Time)=='character'){df$Group.End.Time <- as.POSIXlt(df$Group.End.Time)}
  
  df <- df %>% mutate_at(c('Record.Start.Time', 'Group.Start.Time','Group.End.Time', 'Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), as_hms)
  
  # some of the files do not yet have the small groups start/end time manually verified.
  # fill in Timestamps of small group start/end using Group.Start.Time when missing the timestamp
  df$Timestamp.of.Small.Group.Start[is.na(df$Timestamp.of.Small.Group.Start)] <- as_hms(df$Group.Start.Time[is.na(df$Timestamp.of.Small.Group.Start)] - df$Record.Start.Time[is.na(df$Timestamp.of.Small.Group.Start)])
  
  df$Timestamp.of.Small.Group.End[is.na(df$Timestamp.of.Small.Group.End)] <- as_hms(df$Group.End.Time[is.na(df$Timestamp.of.Small.Group.End)] - df$Record.Start.Time[is.na(df$Timestamp.of.Small.Group.End)])
  
  # replace negative timestamps with 0 (this means smallgroup started before recording)
  df$Timestamp.of.Small.Group.Start[df$Timestamp.of.Small.Group.Start <0] <- hms(0,0,0)
  
  # Drop rows which still don't have timestamps for both start and end of small groups
  df <- df%>% drop_na(c(Timestamp.of.Small.Group.Start, Timestamp.of.Small.Group.End, Names.of.Students))
  

  df$Small.Group.Duration <- df$Timestamp.of.Small.Group.End-df$Timestamp.of.Small.Group.Start 
  
  stats.wide.SGduration <-c(stats.wide.SGduration, unlist(df$Small.Group.Duration))

   # Drop rows with insufficient SG duration
  df <- df %>% filter(Small.Group.Duration>= opts.Duration)
  
# drop rows with issues - do this once Cher says thecolumn has been updated
 df <- df %>% filter(Issues..0.No..1.Yes. == F)
if (nrow(df) < opts.NperTeacher) {print('INSUFFICIENT AUDIO TO GENERATE REQUESTED N SAMPLES') 
  next}
  
  # randomly choose rows for this teacher
  samp_i <- sample(nrow(df), opts.NperTeacher, replace=F)
  sample_this <- df[samp_i,]
  
  # randomly generate sample start times for each row
  for (s in 1:nrow(sample_this)){
    thisrow <- sample_this[s,]
    sample_this$sample_start[s] <- hms(round(runif(1, as.duration(thisrow$Timestamp.of.Small.Group.Start), as.duration(thisrow$Timestamp.of.Small.Group.End-opts.Duration))))
    sample_this$sample_end[s] <- as_hms(sample_this$sample_start[s]+hms(opts.Duration))
    
  }
  sample_this$sample_start <- as_hms(sample_this$sample_start)
  sample_this$sample_end <- as_hms(sample_this$sample_end)
  
  sample_all <- bind_rows(sample_all, sample_this)
  
}

# sample_all$Names.of.Students <- lapply(sample_all$Names.of.Students,paste,collapse = ", ")
sample_all <- sample_all %>%  mutate(Names.of.Students = gsub("\n", ", ", Names.of.Students))

sample_all <- sample_all %>% select(c(Teacher, Period, Lesson.., Name.of.File, URL.to.File, sample_start, sample_end, everything()))
sample_all %>% write.csv('samples_wide_2021-12-14.csv')

stats.wide.SGcount = nrow(stats.wide.SGduration)
stats.wide.SGduration.total = duration(sum(unlist(stats.wide.SGduration),na.rm=T))
stats.wide.SGduration.mean = duration(mean(unlist(stats.wide.SGduration),na.rm=T))
stats.wide.SGduration.sd = duration(sd(unlist(stats.wide.SGduration),na.rm=T))
print(stats.wide.SGcount.total)
print(stats.wide.SGduration.total)
print(stats.wide.SGduration.mean)
print(stats.wide.SGduration.sd)

```

FOCUSSED SAMPLE
Crystal Q2 video
```{r}
dtypes = c('list', 'text', 'text', 'text', 'text', 'text', 'text',  'text','date','guess','guess','guess', 'guess','text','text','guess','guess','logical','text')

 df <- read_xlsx('../Data File Catalog_2021-12-13.xlsx', sheet = 'Sample 1 - Focused', na=c('','NA','Unknown'), col_types = dtypes, trim_ws=T)
  names(df) <- names(df) %>% make.names() 

  df <- df%>% drop_na(c(Timestamp.of.Small.Group.Start, Timestamp.of.Small.Group.End, Student.in.Group))

  df <- df %>% mutate_at(c( 'Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), as_hms)

  df$Small.Group.Duration <- df$Timestamp.of.Small.Group.End-df$Timestamp.of.Small.Group.Start 
  # Drop rows with insufficient SG duration
  df <- df %>% filter(Small.Group.Duration>= opts.Duration)
  
 # drop rows with issues
 df$Issues..0.No..1.Yes.[is.na(df$Issues..0.No..1.Yes.)] <- FALSE # if not true, assume false
 df <- df %>% filter(Issues..0.No..1.Yes. == F)
  
 sample_this <- df # generate samples for all rows
  
  # randomly generate sample start times for each row
  for (s in 1:nrow(sample_this)){
    thisrow <- sample_this[s,]
    sample_this$sample_start[s] <- hms(round(runif(1, as.duration(thisrow$Timestamp.of.Small.Group.Start), as.duration(thisrow$Timestamp.of.Small.Group.End-opts.Duration))))
    sample_this$sample_end[s] <- as_hms(sample_this$sample_start[s]+hms(opts.Duration))
    
  }
  sample_this$sample_start <- as_hms(sample_this$sample_start)
  sample_this$sample_end <- as_hms(sample_this$sample_end)
  
sample_this <- sample_this %>%  mutate(Student.in.Group = gsub("\n", ", ", Student.in.Group))

sample_this %>% write.csv('samples_focused_2021-12-14.csv')

stats.focused.SGduration.total = dseconds(sum(as.numeric(df$Small.Group.Duration),na.rm=T))
stats.focused.SGduration.mean = dseconds(mean(as.numeric(df$Small.Group.Duration),na.rm=T))
stats.focused.SGduration.sd = dseconds(sd(as.numeric(df$Small.Group.Duration),na.rm=T))
print(stats.focused.SGduration.total)
print(stats.focused.SGduration.mean)
print(stats.focused.SGduration.sd)
```




# Generate 5*1-minute samples for Crystal's video, in center of small-group range.
In center of range:
- Find exact midpoint of small-group 
- Choose a range of 5 minutes which includes this midpoint but does not hang over the ends of the recording
- if SG duration < 5 min, use whole range



```{r}
sample_5x1 <- list()
count=0
opts.Duration <- 300
opts.ChunkBy <- 60
opts.nChunk = opts.Duration/opts.ChunkBy
 # randomly generate sample start times for each row
  for (s in 1:nrow(df)){
    thisrow <- df[s,]
   if (hms(opts.Duration) > as_hms(thisrow$Small.Group.Duration)){
   print('***WARNING*** insufficient audio')}
    
   sample_start_block <- hms(round(as.duration(
     runif(
       1,
       max(as_hms(thisrow$Timestamp.of.Small.Group.Start+ as_hms(0.5*thisrow$Small.Group.Duration) - as_hms(opts.Duration)), thisrow$Timestamp.of.Small.Group.Start),
       min(as_hms(thisrow$Timestamp.of.Small.Group.Start+ as_hms(0.5*thisrow$Small.Group.Duration)), as_hms(thisrow$Timestamp.of.Small.Group.End-as_hms(opts.Duration)) ))
   )))

   
   for (i in 1:(opts.nChunk)){
     count=count+1
     rowtoadd <- thisrow %>% select(c('Teacher', 'Period', 'Lesson..', 'Name.of.File', 'URL.to.File','Timestamp.of.Small.Group.Start','Timestamp.of.Small.Group.End','Small.Group.Duration' ))
     rowtoadd$Small.Group.Duration <- as_hms(rowtoadd$Small.Group.Duration)
     rowtoadd$sample_start<- as_hms(sample_start_block + hms(opts.ChunkBy*(i-1)))
     rowtoadd$sample_end<- as_hms(rowtoadd$sample_start+hms(opts.ChunkBy))
     sample_5x1[[count]] <- rowtoadd
   }
    
      
  }
sample_5x1 <- bind_rows(sample_5x1)%>% write.csv('../annotation/samples_focussed_5inCenter_2021-12-16.csv')
```