---
title: "chooseRandomSGSamples"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
# Load/Install Packages
ipak <- function(pkg){
  new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
  if (length(new.pkg)) 
    install.packages(new.pkg, dependencies = TRUE)
  sapply(pkg, require, character.only = TRUE)
}
packages <- c('sjPlot', 'reshape2', 'magrittr', 'data.table', 'gridExtra', 'ggplot2','stringr','readxl','tidyverse', 'dplyr','tidyr','strex','tibble','chron','lubridate','anytime','hms','stringr','openxlsx')
ipak(packages)

```


Given the data catalog (https://docs.google.com/spreadsheets/d/1Xs5jM9yGRmRbrSxjrRFIUpzbfb-MdcGOi_FyJen6MXk)
Generate random 5-minute samples under the following constraints
- must have a small-group start and end time
- small-group duration must be greater than sample duration
- must sample evenly across teachers
- set number of samples per period (i.e. set of students in class)
- must sample randomly across groups
- must sample randomly across lessons (i.e. content)

In center of range:
- Find exact midpoint of small-group 
- Choose a range of 5 minutes which includes this midpoint but does not hang over the ends of the recording
- if SG duration < 5 min, use whole range
- exclude enrollment - SG is trimmed to largest portion before or after enrollment


```{r wideSample1}
opts.NperPeriod = 1
opts.Duration = 300 # seconds

sheets <- excel_sheets('../Data File Catalog_2022-02-08.xlsx')
audio_sheets <- sheets %>% str_subset(pattern = "Audio") %>% str_subset(pattern = "Heading", negate = T) 

sample_all <-  list()
stats.wide.SGduration <- list()
count=0
dtypes = c('text', 'text',
           'text', 'text',
           'text', 'text',
           'text',  'date',   'date','date',
           'date','guess','guess','guess',
           'guess','date',  'list','text','text','guess','guess','logical','text', 'guess','guess','guess','guess','guess','guess','guess','guess','guess')

for (sheet in audio_sheets){
  count=count+1
  df <- read_xlsx('../Data File Catalog_2022-02-08.xlsx', sheet = sheet, na=c('','NA','Unknown'), col_types = dtypes, trim_ws=T)
  names(df) <- names(df) %>% make.names() 
  if (nrow(df) == 0) next
  
  df <- df %>% filter(!grepl('End',Group.End.Time))
  
  if (class(df$Group.End.Time)=='character'){df$Group.End.Time <- as.POSIXlt(df$Group.End.Time)}
  
  df <- df %>% mutate_at(c('Record.Start.Time', 'Group.Start.Time','Group.End.Time', 'Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), as_hms)
  
  # some of the files do not yet have the small groups start/end time manually verified.
  # fill in Timestamps of small group start/end using Group.Start.Time when missing the timestamp
  df$Timestamp.of.Small.Group.Start[is.na(df$Timestamp.of.Small.Group.Start)] <- as_hms(df$Group.Start.Time[is.na(df$Timestamp.of.Small.Group.Start)] - df$Record.Start.Time[is.na(df$Timestamp.of.Small.Group.Start)])
  df$Timestamp.of.Small.Group.End[is.na(df$Timestamp.of.Small.Group.End)] <- as_hms(df$Group.End.Time[is.na(df$Timestamp.of.Small.Group.End)] - df$Record.Start.Time[is.na(df$Timestamp.of.Small.Group.End)])
  
  # replace negative timestamps with 0 (this means smallgroup started before recording)
  df$Timestamp.of.Small.Group.Start[df$Timestamp.of.Small.Group.Start <0] <- hms(0,0,0)
  
  # Drop rows which still don't have timestamps for both start and end of small groups
  df <- df%>% drop_na(c(Timestamp.of.Small.Group.Start, Timestamp.of.Small.Group.End, Names.of.Students))
  df$Small.Group.Duration <- as_hms(df$Timestamp.of.Small.Group.End-df$Timestamp.of.Small.Group.Start )
  
  # Remove enrollment from small group and adjust start/end time to longest uninterrupted SG duration
  for (s in 1:nrow(df)){
    thisrow =  df[s,]
    if (!is.na(thisrow$'Timestamp.of.Enrollment.Start')){
      if(thisrow$'Timestamp.of.Enrollment.Start'<thisrow$'Timestamp.of.Small.Group.End'){
        if(thisrow$'Timestamp.of.Enrollment.End'> thisrow$'Timestamp.of.Small.Group.Start'){
          print('Small-group contains enrollment')
          # if enrollment overlaps SG start, trim start of SG
          if (thisrow$'Timestamp.of.Enrollment.Start' < thisrow$'Timestamp.of.Small.Group.Start'){
            print(' trimming small-group START to exclude enrollment')
            thisrow$Timestamp.of.Small.Group.Start = thisrow$Timestamp.of.Enrollment.End
          }
          # if enrollment overlaps SG end, trim end of SG
          if (thisrow$'Timestamp.of.Enrollment.End' > thisrow$'Timestamp.of.Small.Group.End'){
            print(' trimming small-group END to exclude enrollment')
            thisrow$Timestamp.of.Small.Group.End = thisrow$Timestamp.of.Enrollment.Start
          }
          else{        # if enrollment is in middle, trim SG to largest uninterrupted interval
            i1= thisrow$Timestamp.of.Enrollment.Start- thisrow$Timestamp.of.Small.Group.Start
            #   print(paste0(thisrow$Name.of.File,': i1 = ', i1))
            i2= thisrow$Timestamp.of.Small.Group.End- thisrow$Timestamp.of.Enrollment.End
            # print(paste0(thisrow$Name.of.File,': i2 = ', i2))
            
            if (i1>i2 ){
              thisrow$Timestamp.of.Small.Group.End = thisrow$Timestamp.of.Enrollment.Start
              print(paste0('taking SG from before enrollment - duration ',i1, 'sec'))
            }else{
              thisrow$Timestamp.of.Small.Group.Start = thisrow$Timestamp.of.Enrollment.End
              print(paste0('taking SG from after enrollment - duration ', i2, 'sec'))
            }
            
          }
        }
      }
    }
    thisrow$Small.Group.Duration <- thisrow$Timestamp.of.Small.Group.End-thisrow$Timestamp.of.Small.Group.Start 
    df[s,] = thisrow
  }
  stats.wide.SGduration <-c(stats.wide.SGduration, unlist(df$Small.Group.Duration))
  
  # Drop rows with insufficient SG duration
  df <- df %>% filter(Small.Group.Duration>= opts.Duration)
  
  # randomly choose rows for this teacher, grouping by period
  df <- df %>% group_by(Period) %>% slice_sample(n=opts.NperPeriod)
  sample_all[[count]] = df # append to list of teacher-wise Dfs
}
sample_all = bind_rows(sample_all)
sample_all <- sample_all %>%  mutate(Names.of.Students = gsub("\n", ", ", Names.of.Students))

# CHOOSE RANDOM SAMPLE TIMES FOR SELECTED SESSIONS
count=0
opts.Duration <- 300
opts.ChunkBy <- 300 # same as opts.Duration for one single sample 
opts.nChunk = opts.Duration/opts.ChunkBy
opts.repeats = 5
# randomly generate sample start times for each row
for (k in 1:opts.repeats){
  sample <- list()
  
  for (s in 1:nrow(sample_all)){
    thisrow <- sample_all[s,]
    
    
    if (hms(opts.Duration) > as_hms(thisrow$Small.Group.Duration)){
      print(paste0('***WARNING*** insufficient audio for ' , thisrow$Name.of.File))}
    
    sample_start_block <- hms(round(as.duration(
      runif(
        1,
        max(as_hms(thisrow$Timestamp.of.Small.Group.Start+ as_hms(0.5*thisrow$Small.Group.Duration) - as_hms(opts.Duration)), thisrow$Timestamp.of.Small.Group.Start),
        min(as_hms(thisrow$Timestamp.of.Small.Group.Start+ as_hms(0.5*thisrow$Small.Group.Duration)), as_hms(thisrow$Timestamp.of.Small.Group.End-as_hms(opts.Duration)) ))
    )))
    
    
    for (i in 1:(opts.nChunk)){
      count=count+1
      rowtoadd <- thisrow %>% select(c('Teacher', 'Period', 'Lesson..', 'Name.of.File', 'URL.to.File','Timestamp.of.Small.Group.Start','Timestamp.of.Small.Group.End','Small.Group.Duration' ,
                                       'Timestamp.of.Enrollment.Start','Timestamp.of.Enrollment.End'))
      rowtoadd$Small.Group.Duration <- as_hms(rowtoadd$Small.Group.Duration)
      rowtoadd$sample_start<- as_hms(sample_start_block + hms(opts.ChunkBy*(i-1)))
      rowtoadd$sample_end<- as_hms(rowtoadd$sample_start+hms(opts.ChunkBy))
      sample[[count]] <- rowtoadd
    }
    
    
  }
  sample <- bind_rows(sample)%>% arrange(Name.of.File) %>% data.frame()
  sample <- sample%>% rename(!!paste0('sample_start_',k) := 'sample_start')
  sample <- sample%>% rename(!!paste0('sample_end_',k) := 'sample_end')
  if (k==1) {
    ksamples=sample}else{
      ksamples <-  merge(ksamples, sample, by=c('Teacher', 'Period', 'Lesson..', 'Name.of.File', 'URL.to.File','Timestamp.of.Small.Group.Start','Timestamp.of.Small.Group.End','Small.Group.Duration' ,
                                                'Timestamp.of.Enrollment.Start','Timestamp.of.Enrollment.End'))
    }
}
ksamples %>% write.csv(paste0('../annotation/samples_wide_5inCenter_2022-02-08.csv'))







```

FUNCTIONS
```{r functions}
fix_missing_SG_timestamps<-function(df){
    # if (class(df$Group.Start.Time)=='character'){df$Group.Start.Time <- as.POSIXlt(df$Group.Start.Time)}
    # if (class(df$Group.End.Time)=='character'){df$Group.End.Time <- as.POSIXlt(df$Group.End.Time)}
    
    # the only way i could get the time format properly is to convert numeric->times->character->hms... ugh
    df <- df %>% mutate_at(c('Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), as.numeric)
    df <- df %>% mutate_at(c('Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), chron::times)
    df <- df %>% mutate_at(c('Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), as.character)
    df <- df %>% mutate_at(c('Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), as.hms)
    
    
    
    df <- df %>% mutate_at(c( 'Record.Start.Time', 'Group.Start.Time','Group.End.Time' ), as.numeric)
    df <- df %>% mutate_at(c( 'Record.Start.Time', 'Group.Start.Time','Group.End.Time' ), chron::times)
    df <- df %>% mutate_at(c( 'Record.Start.Time', 'Group.Start.Time','Group.End.Time' ), as.character)
    df <- df %>% mutate_at(c( 'Record.Start.Time', 'Group.Start.Time','Group.End.Time' ), as.hms)
    
    # some of the files do not yet have the small groups start/end time manually verified.
    # fill in Timestamps of small group start/end using Group.Start.Time when missing the timestamp
    df$Timestamp.of.Small.Group.Start[is.na(df$Timestamp.of.Small.Group.Start)] <- df$Group.Start.Time[is.na(df$Timestamp.of.Small.Group.Start)] - df$Record.Start.Time[is.na(df$Timestamp.of.Small.Group.Start)]
    df$Timestamp.of.Small.Group.End[is.na(df$Timestamp.of.Small.Group.End)] <- df$Group.End.Time[is.na(df$Timestamp.of.Small.Group.End)] - df$Record.Start.Time[is.na(df$Timestamp.of.Small.Group.End)]
    
    # if still no timestamp of small group end, assume end of recordign
    
    # replace negative timestamps with 0 (this means smallgroup started before recording)
    df$Timestamp.of.Small.Group.Start[df$Timestamp.of.Small.Group.Start <0] <- hms(0,0,0)
    
    # Drop rows which still don't have timestamps for both start and end of small groups
    df <- df%>% drop_na(c(Timestamp.of.Small.Group.Start, Timestamp.of.Small.Group.End))
    df$Small.Group.Duration <- as_hms(df$Timestamp.of.Small.Group.End-df$Timestamp.of.Small.Group.Start )
  return(df)
}

#####
remove_enrollment <- function(df){
  # Remove enrollment from small group and adjust start/end time to longest uninterrupted SG duration
  for (s in 1:nrow(df)){
    thisrow =  df[s,]
    if (!is.na(thisrow$'Timestamp.of.Enrollment.Start')){
      if(thisrow$'Timestamp.of.Enrollment.Start'<thisrow$'Timestamp.of.Small.Group.End'){
        if(thisrow$'Timestamp.of.Enrollment.End'> thisrow$'Timestamp.of.Small.Group.Start'){
          print('Small-group contains enrollment')
          # if enrollment overlaps SG start, trim start of SG
          if (thisrow$'Timestamp.of.Enrollment.Start' < thisrow$'Timestamp.of.Small.Group.Start'){
            print(' trimming small-group START to exclude enrollment')
            thisrow$Timestamp.of.Small.Group.Start = thisrow$Timestamp.of.Enrollment.End
          }
          # if enrollment overlaps SG end, trim end of SG
          if (thisrow$'Timestamp.of.Enrollment.End' > thisrow$'Timestamp.of.Small.Group.End'){
            print(' trimming small-group END to exclude enrollment')
            thisrow$Timestamp.of.Small.Group.End = thisrow$Timestamp.of.Enrollment.Start
          }
          else{        # if enrollment is in middle, trim SG to largest uninterrupted interval
            i1= thisrow$Timestamp.of.Enrollment.Start- thisrow$Timestamp.of.Small.Group.Start
            #   print(paste0(thisrow$Name.of.File,': i1 = ', i1))
            i2= thisrow$Timestamp.of.Small.Group.End- thisrow$Timestamp.of.Enrollment.End
            # print(paste0(thisrow$Name.of.File,': i2 = ', i2))
            
            if (i1>i2 ){
              thisrow$Timestamp.of.Small.Group.End = thisrow$Timestamp.of.Enrollment.Start
              print(paste0('taking SG from before enrollment - duration ',i1, 'sec'))
            }else{
              thisrow$Timestamp.of.Small.Group.Start = thisrow$Timestamp.of.Enrollment.End
              print(paste0('taking SG from after enrollment - duration ', i2, 'sec'))
            }
            
          }
        }
      }
    }
    thisrow$Small.Group.Duration <- thisrow$Timestamp.of.Small.Group.End-thisrow$Timestamp.of.Small.Group.Start 
    df[s,] <- thisrow
  }
  return(df)
}

########
sample_middle_third <- function(thisrow, opts.Duration = 300, opts.Nwin=5){
  
  if (hms(opts.Duration) > as_hms(thisrow$Small.Group.Duration)){
    print(paste0('***WARNING*** insufficient audio for ' , thisrow$Name.of.File))
    return(NULL)}else{
      
      for(k in 1:opts.Nwin){  
        sample_start <- hms(round(as.duration(
          runif(
            1,
            max(as_hms(thisrow$Timestamp.of.Small.Group.Start+ as_hms(0.5*thisrow$Small.Group.Duration) - as_hms(opts.Duration)), thisrow$Timestamp.of.Small.Group.Start),
            min(as_hms(thisrow$Timestamp.of.Small.Group.Start+ as_hms(0.5*thisrow$Small.Group.Duration)), as_hms(thisrow$Timestamp.of.Small.Group.End-as_hms(opts.Duration)) ))
        )))
        
        thisrow$sample_start<- as_hms(sample_start )
        thisrow$sample_end<- as_hms(sample_start+ hms(opts.Duration))
        thisrow <- thisrow%>% rename(!!paste0('sample_start_',k) := 'sample_start')
        thisrow <- thisrow%>% rename(!!paste0('sample_end_',k) := 'sample_end')
      }
      return(thisrow)
    }
}
```



# Wide Sample March 2022
Random sample 1 video per student across all teachers 
Use audio only if no group video available for that student
1 video can represent 2-4 students - we don't want them appearing multiple times
As before, draw 5 random windows from small group for each video
repeat algorithm x2-3
```{r wideSample2}
opts.Niter = 3 # repeats of sampling algorithm
opts.Nwin = 5 # how many random sample times per selected video
opts.Duration = 300 # seconds, duration of small group
catalog_file <- '../Data File Catalog_2022-04-01.xlsx'

# set column names to use for media sheets
mediacols <- c(  "Teacher" ,"Period" , "Lesson.#",  "Name.of.File" , "URL.to.File" , 'Equipment.Used', "Record.Start.Time" ,"Group.Start.Time","Group.End.Time", "Timestamp.of.Small.Group.Start", "Timestamp.of.Small.Group.End"  , "Timestamp.of.Enrollment.Start" ,"Timestamp.of.Enrollment.End" , "Student.IDs"  , "Useable.(0=no,.1=yes)")

sheets <- excel_sheets(catalog_file)
audio_sheets <- sheets %>% str_subset(pattern = " A") %>% str_subset(pattern = "Heading", negate = T) 
video_sheets <- sheets %>% str_subset(pattern = " V - Group") %>% str_subset(pattern = "Heading", negate = T) 

students <- read_xlsx(catalog_file, 'WIP Consents WRecordings') %>% 
  select(-contains('...')) %>% 
  pivot_longer(contains('Consent'), names_to='consent_type', values_to='consented') %>% 
  filter(!grepl('Assess',consent_type)) %>% filter(consented=='YES') %>% 
  mutate(consented=consented=='YES') %>% 
  pivot_wider(names_from = consent_type, values_from=consented, values_fill=F) %>% 
  mutate(video_consent=`Student Consent Video` & `Parent Consent Video`, audio_consent=`Student Consent Audio` & `Parent Consent Audio`) %>% 
  filter(video_consent|audio_consent) %>% 
  mutate(`Student ID` = sprintf("%03d",as.integer(`Student ID`))) %>% 
  filter(!grepl(  'NA',`Student ID`)) 

names(students) <- make.names(names(students))

student_list = students$Student.ID
teacher_list = unique(students$Teacher)
n_students_wide <- list()
for (k in 1:opts.Niter){
  widesample <- list()
  count=0
  student_remaining <- student_list
  
  for (t in 1:length(teacher_list)){
    teacher = teacher_list[t]
    print(paste('----Teacher:',teacher))
    class_students = students %>% filter(Teacher == teacher)
    # read audio and video df
    asheet <- audio_sheets[grepl(teacher,audio_sheets)]
    vsheet <- video_sheets[grepl(teacher,video_sheets)]
    has_A <- length(asheet)>0
    has_V <- length(vsheet)>0
    if (has_V){
          if(length(vsheet)>1){ 
            video=list()
            for( v in 1:length(vsheet)){
      video[[v]] <- read.xlsx(catalog_file, sheet=vsheet[v], detectDates=T,na.strings = "NA") %>% select(mediacols) %>% mutate_at(vars(contains('Timestamp')), as.numeric) %>% mutate_at(vars(Student.IDs), as.character)
            }
            video <- bind_rows(video)
            }else{
            video <- read.xlsx(catalog_file, sheet=vsheet, detectDates=T,na.strings = "NA") %>% select(mediacols)
            }

      # video[video=='NA'] <- NA
      print(paste('n video files total: ' , nrow(video)))
      
      names(video) <- make.names(names(video))
      video <- video %>% rename_at(vars(grep("Useable",names(.))), ~'useable')
      video <- video %>% filter(useable==1 & !is.na(Student.IDs))
      print(paste('...n video files useable: ' , nrow(video)))
      
      # filter out any rows without consent for all students
      video <- video %>%  mutate(listStudentID = str_split(Student.IDs, boundary('word')))
      video <-  video %>% mutate(all_consented = all(unlist(listStudentID) %in% c(student_list, 'NA')))
      #   video <- video %>% filter(all_consented) %>% filter(!listStudentID=='NA')
      print(paste('...n video files consented: ' , nrow(video)))
      
      
      # repair timestamps & filter to those with SG timestamps
      video <- fix_missing_SG_timestamps(video)
      print(paste('...n video files with SG timestamps: ' , nrow(video)))
      
      if(nrow(video)==0){has_V=F}
      
    }
    if (has_A){
                if(length(asheet)>1){ 
            audio=list()
            for( a in 1:length(asheet)){
      audio[[a]] <- read.xlsx(catalog_file, sheet=asheet[a], detectDates=T,na.strings = "NA") %>% select(mediacols) %>% mutate_at(vars(contains('Timestamp')), as.numeric)  %>% mutate_at(vars(Student.IDs), as.character) 
            }
            audio <- bind_rows(audio)
            }else{
            audio <- read.xlsx(catalog_file, sheet=asheet, detectDates=T,na.strings = "NA") %>% select(mediacols)
            }

            names(audio) <- make.names(names(audio))
      print(paste('n audio files total: ' , nrow(audio)))
      
      audio <- audio %>% rename_at(vars(grep("Useable",names(.))), ~'useable')
      audio <- audio %>% filter(useable==1 & !is.na(Student.IDs))
      print(paste('...n audio files useable: ' , nrow(audio)))
      
      # filter out any rows without consent for all students
      audio <- audio %>%  mutate(listStudentID = str_split(Student.IDs, boundary('word')))
      audio <-  audio %>% mutate(all_consented = all(unlist(listStudentID) %in% c(student_list, 'NA')))
      #  audio <- audio %>% filter(all_consented) %>% filter(!listStudentID=='NA')
      print(paste('...n audio files consented: ' , nrow(audio)))
      
      # repair timestamps & filter to those with SG timestamps
      audio <- fix_missing_SG_timestamps(audio)
      print(paste('...n audio files with SG timestamps: ' , nrow(audio)))
      
      if(nrow(audio)==0){has_A=F}
    }
    if(!has_A & !has_V){print(paste0('!! No usable (consented, timestamped) media for teacher ', teacher))
      next}
    
    for (s in 1:nrow(class_students)){ # loop over students in this class
      
      # check if student has already appeared in a selected video
      studentID <- class_students$Student.ID[s]
      
      if (!studentID %in% student_remaining){
        print(paste0('Student already appeared in a selected video: ', studentID))
        next}
      
      media <- NULL
      # Use video if poss, otherwise audio
      if(has_V & class_students$video_consent[s]){
        media <-video %>% filter(grepl( studentID,listStudentID))}
      if(is.null(media) & has_A & class_students$audio_consent[s]){
        media <-audio %>% filter(grepl( studentID,listStudentID))}
      
      
      if (nrow(media)==0){print(paste('no consented media for Student',studentID)) ;
        next}
      print(paste0(nrow(media), ' media files found for Student ',studentID))
      
      # exclude enrollment from widesample
      media <- remove_enrollment(media)
      
      # check for sufficient audio
      media <- media %>% filter(Small.Group.Duration >= hms(opts.Duration) )
      if (nrow(media)==0){print(paste('no consented media for Student',studentID)) ;
        next}
      
      # filter to include only Yeti if available
      media_yeti <- media %>% filter(grepl('yeti|Yeti', Equipment.Used))
      print(paste('n with Yeti',nrow(media_yeti), 'out of',nrow(media)))
      if (nrow(media_yeti) >0 ){media <- media_yeti}
      
      # choose a file for this student
      thisrow <- media[sample(nrow(media),1), ]
      
      # draw samples from within the small group middle third
      thisrow <- sample_middle_third(thisrow, opts.Duration, opts.Nwin)
      
      # remove students in selected media from list
      student_remaining <- setdiff(student_remaining, unlist(thisrow$listStudentID))
      
      # select consistent variables 
      thisrow <- thisrow %>% select(c(Teacher, Period, Lesson.., Name.of.File, URL.to.File, Student.IDs, contains('sample_'))) %>% rename(Lesson = Lesson..)
      
      # force classes
      thisrow$Period <- as.character(thisrow$Period)
      thisrow$Lesson <- as.character(thisrow$Lesson)
      
      # add row
      count=count+1
      widesample[[count]] <- thisrow
      
      rm(media, student_audio, student_video)  
    }# student
    rm(audio,video)
  }# teacher
  widesample <- bind_rows(widesample) %>% data.frame()
  widesample %>% write.csv(paste0('../annotation/samples_wide_5inCenter_2022-03-20_',k,'.csv'))
  n_students_wide[k] <- length(student_list)-length(student_remaining)

} #k
```

FOCUSSED SAMPLE v1
Crystal Q2 video
```{r}
dtypes = c('text', 'text', 'text', 'text', 'text', 'text', 'text',  'text','date','guess','guess','guess', 'guess','text','text','guess','guess','text','text')

df <- read_xlsx('../Data File Catalog_2022-01-26.xlsx', sheet = 'Sample 1 - Crystal Focused', na=c('','NA','Unknown'), col_types = dtypes, trim_ws=T)
names(df) <- names(df) %>% make.names() 

df <- df%>% filter(!grepl('missing REV transcript|consent issue', Sample.Comments))

df <- df %>% mutate_at(c( 'Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), as_hms)

all_students = paste(df %>% select(Student.in.Group)%>% unlist(use.names = FALSE), collapse='\n') %>% strsplit(split='\n')
all_students = all_students[1] %>% unlist() %>% unique() 
n_students = length(all_students)

```

FOCUSSED SAMPLE v2
Crystal Q2 video
random timestamp, no restriciton
```{r}
#dtypes = c('list', 'text', 'text', 'text', 'text', 'text', 'text',  'text','date','guess','guess','guess', 'guess','text','text','guess','guess','logical','text')
dtypes = c('list', 'text', 'text', 'text', 'text', 'text', 'text',  'text','date','guess','guess','guess', 'guess','text')

df <- read_xlsx('../Data File Catalog_2022-02-08.xlsx', sheet = 'Sample 1v2 - Crystal Focused', na=c('','NA','Unknown'), range = cell_cols(1:14), col_types = dtypes, trim_ws=T)
names(df) <- names(df) %>% make.names() 

df <- df%>% drop_na(c(Timestamp.of.Small.Group.Start, Timestamp.of.Small.Group.End, Student.in.Group))

df <- df %>% mutate_at(c( 'Timestamp.of.Small.Group.Start', 'Timestamp.of.Small.Group.End', 'Timestamp.of.Enrollment.Start', 'Timestamp.of.Enrollment.End' ), as_hms)

n_unique_groups = df %>% group_by(Student.in.Group) %>% summarise(n())

df$Small.Group.Duration <- df$Timestamp.of.Small.Group.End-df$Timestamp.of.Small.Group.Start 
# #Drop rows with insufficient SG duration
#df <- df %>% filter(Small.Group.Duration>= opts.Duration)

# # drop rows with issues
# df$Issues..0.No..1.Yes.[is.na(df$Issues..0.No..1.Yes.)] <- FALSE # if not true, assume false
# df <- df %>% filter(Issues..0.No..1.Yes. == F)

sample_this <- df # generate samples for all rows

# randomly generate sample start times for each row, no resrtrictions
for (s in 1:nrow(sample_this)){
  thisrow <- sample_this[s,]
  sample_this$sample_start[s] <- hms(round(runif(1, as.duration(thisrow$Timestamp.of.Small.Group.Start), as.duration(thisrow$Timestamp.of.Small.Group.End-opts.Duration))))
  sample_this$sample_end[s] <- as_hms(sample_this$sample_start[s]+hms(opts.Duration))
  
}
sample_this$sample_start <- as_hms(sample_this$sample_start)
sample_this$sample_end <- as_hms(sample_this$sample_end)

sample_this <- sample_this %>%  mutate(Student.in.Group = gsub("\n", ", ", Student.in.Group))

#sample_this %>% write.csv('samples_focused_2021-01-26.csv')

stats.focused.SGduration.total = dseconds(sum(as.numeric(df$Small.Group.Duration),na.rm=T))
stats.focused.SGduration.mean = dseconds(mean(as.numeric(df$Small.Group.Duration),na.rm=T))
stats.focused.SGduration.sd = dseconds(sd(as.numeric(df$Small.Group.Duration),na.rm=T))
print(stats.focused.SGduration.total)
print(stats.focused.SGduration.mean)
print(stats.focused.SGduration.sd)
```




# Generate samples for Crystal's video, in center of small-group range, excluding enrollment
In center of range:
- Find exact midpoint of small-group 
- Choose a range of 5 minutes which includes this midpoint but does not hang over the ends of the recording
- if SG duration < 5 min, use whole range



```{r}
sample <- list()
count=0
opts.Duration <- 300
opts.ChunkBy <- 300 # same as opts.Duration for one single sample 
opts.nChunk = opts.Duration/opts.ChunkBy
opts.repeats = 5
# randomly generate sample start times for each row
for (k in 1:opts.repeats){
  sample <- list()
  
  for (s in 1:nrow(df)){
    thisrow <- df[s,]
    
    # exclude enrollment portion
    if (!is.na(thisrow$'Timestamp.of.Enrollment.Start')){
      if(thisrow$'Timestamp.of.Enrollment.Start'<thisrow$'Timestamp.of.Small.Group.End'){
        if(thisrow$'Timestamp.of.Enrollment.End'> thisrow$'Timestamp.of.Small.Group.Start'){
          print('Small-group contains enrollment')
          # if enrollment overlaps SG start, trim start of SG
          if (thisrow$'Timestamp.of.Enrollment.Start' < thisrow$'Timestamp.of.Small.Group.Start'){
            print(' trimming small-group START to exclude enrollment')
            thisrow$Timestamp.of.Small.Group.Start = thisrow$Timestamp.of.Enrollment.End
          }
          # if enrollment overlaps SG end, trim end of SG
          if (thisrow$'Timestamp.of.Enrollment.End' > thisrow$'Timestamp.of.Small.Group.End'){
            print(' trimming small-group END to exclude enrollment')
            thisrow$Timestamp.of.Small.Group.End = thisrow$Timestamp.of.Enrollment.Start
          }
          else{        # if enrollment is in middle, trim SG to largest uninterrupted interval
            i1= thisrow$Timestamp.of.Enrollment.Start- thisrow$Timestamp.of.Small.Group.Start
            print(paste0(thisrow$Name.of.File,': i1 = ', i1))
            i2= thisrow$Timestamp.of.Small.Group.End- thisrow$Timestamp.of.Enrollment.End
            print(paste0(thisrow$Name.of.File,': i2 = ', i2))
            
            if (i1>i2 ){
              thisrow$Timestamp.of.Small.Group.End = thisrow$Timestamp.of.Enrollment.Start
              print(paste0('taking SG from before enrollment - duration ',i1, 'sec'))
            }else{
              thisrow$Timestamp.of.Small.Group.Start = thisrow$Timestamp.of.Enrollment.End
              print(paste0('taking SG from after enrollment - duration ', i2, 'sec'))
            }
            
          }
          # recalcualte the SG duration
          
          
        }
      }
    }
    thisrow$Small.Group.Duration <- thisrow$Timestamp.of.Small.Group.End-thisrow$Timestamp.of.Small.Group.Start 
    
    if (hms(opts.Duration) > as_hms(thisrow$Small.Group.Duration)){
      print(paste0('***WARNING*** insufficient audio for ' , thisrow$Name.of.File))}
    
    sample_start_block <- hms(round(as.duration(
      runif(
        1,
        max(as_hms(thisrow$Timestamp.of.Small.Group.Start+ as_hms(0.5*thisrow$Small.Group.Duration) - as_hms(opts.Duration)), thisrow$Timestamp.of.Small.Group.Start),
        min(as_hms(thisrow$Timestamp.of.Small.Group.Start+ as_hms(0.5*thisrow$Small.Group.Duration)), as_hms(thisrow$Timestamp.of.Small.Group.End-as_hms(opts.Duration)) ))
    )))
    
    
    for (i in 1:(opts.nChunk)){
      count=count+1
      rowtoadd <- thisrow %>% select(c('Teacher', 'Period', 'Lesson..', 'Name.of.File', 'URL.to.File','Timestamp.of.Small.Group.Start','Timestamp.of.Small.Group.End','Small.Group.Duration' ,
                                       'Timestamp.of.Enrollment.Start','Timestamp.of.Enrollment.End'))
      rowtoadd$Small.Group.Duration <- as_hms(rowtoadd$Small.Group.Duration)
      rowtoadd$sample_start<- as_hms(sample_start_block + hms(opts.ChunkBy*(i-1)))
      rowtoadd$sample_end<- as_hms(rowtoadd$sample_start+hms(opts.ChunkBy))
      sample[[count]] <- rowtoadd
    }
    
    
  }
  sample <- bind_rows(sample)%>% arrange(Name.of.File) %>% data.frame()
  sample <- sample%>% rename(!!paste0('sample_start_',k) := 'sample_start')
  sample <- sample%>% rename(!!paste0('sample_end_',k) := 'sample_end')
  if (k==1) {
    ksamples=sample}else{
      ksamples <-  merge(ksamples, sample, by=c('Teacher', 'Period', 'Lesson..', 'Name.of.File', 'URL.to.File','Timestamp.of.Small.Group.Start','Timestamp.of.Small.Group.End','Small.Group.Duration' ,
                                                'Timestamp.of.Enrollment.Start','Timestamp.of.Enrollment.End'))
    }
}
ksamples %>% write.csv(paste0('../annotation/samples_focussed_5inCenter_2022-01-26.csv'))
```